Procurements of the Canadian Government, Runaway Military Contracts

### 2024-11-29 paper/paper.qmd
More TODO's! And TODO Refs

@@

# Web Scraping
These are step by step instructions on how to Web Scrape the IFJ procurement data page, because as of November 2024 there is no easy/automated way of downloading the 330 pages of 1000 rows worth of data.

Note: It is important that docker, java, python and firefox are installed on your machine as RSelenium requires these packages. To download Selenium and create a docker image, open the docker application and search for the Selenium package.

@@

4. The for-loop simply runs "click download -> click next page" process 329 times, however IJF may add more pages so modify total_pages to scrape the number of pages IJF has. In the event of an error mid-way through scraping take note of which page failed to download (page that you are on is printed to the console) and simply set the start of the for-loop. After restarting the loop be sure to verify that the next downloaded page is the correct one, otherwise you will have to restart the process from step 1.

5. Done! Enjoy!

@@

>>>>

```
TODO mention that detwiler makes up 88+% spending of the Space Agency

TODO add pie chart showing top suppliers and other of National defence spending

TODO add small contracts distribution chart

@@

# Web Scraping

These are step by step instructions on how to Web Scrape the IFJ procurement data page, because as of November 2024 there is no easy/automated way of downloading the 330 pages of data.

Note: It is important that docker, java, python and Firefox are installed on your machine as RSelenium requires these packages. To download Selenium and create a docker image, open the docker application and search for the Selenium package for the browser you wish to use, in this case Firefox.

@@

4. The for-loop simply runs "click download -> click next page" process 329 times, however IJF may add more pages so modify total_pages to scrape the number of pages IJF is offering. In the event of an error mid-way through scraping take note of which page failed to download (page that you are on is printed to the console) and simply set the start of the for-loop. After restarting the loop be sure to verify that the next downloaded page is the correct one, otherwise you will have to restart the process from step 1.

5. Done!

@@

TODO Ref RSelenuim
